Carbonate chemistry at Ny-Ålesund

### 2022-08-16 awipev-CO2.Rmd
pCO2 REMOS

pHinsi_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
  scale_x_discrete("Month") +
  scale_y_continuous(substitute("pH"["T"] ~ "at in situ temp."), limits = c(-0.07, 0.03), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.02, parse = TRUE, label = "pH['surface'] > pH['deep']") +
  annotate("text", x = 1.5, y = -0.06, parse = TRUE, label = "pH['surface'] <  pH['deep']") +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
print(pHinsi_delta_plt)
# we look at pHint_tot_sf normalized at 4°C at all depths
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pHint_tot_sf at 4°C vs depth", x = "Depth (m)", y= "pH at 4°C (units)") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group * tmp$montht))

@@

# all deltas
deltas_plt <- sal_delta_plt / temp_delta_plt / den_delta_plt / pH_delta_plt
deltas_plt <- deltas_plt + plot_annotation(tag_levels = 'a')
print(deltas_plt)
ggsave(filename = "figures/deltas.png", plot = deltas_plt, width = 15, height = 20, units = "cm")
```

>>>>

pHinsi_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
  scale_x_discrete("Month") +
  scale_y_continuous(substitute("pH"["T"] ~ "at in situ temp."), limits = c(-0.07, 0.03), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.02, parse = TRUE, label = "pH['surface'] > pH['deep']") +
  annotate("text", x = 1.5, y = -0.06, parse = TRUE, label = "pH['surface'] <  pH['deep']") +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
print(pHinsi_delta_plt)

# we look at pHint_tot_sf normalized at 4°C at all depths
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pHint_tot_sf at 4°C vs depth", x = "Depth (m)", y= "pH at 4°C (units)") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group * tmp$montht))

@@

# we look at pHint_tot_sf normalized at 4°C at all depths
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pHint_tot_sf at 4°C vs depth", x = "Depth (m)", y= "pH at 4°C (units)") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group * tmp$montht))

# we look at pCO2 normalized at 4°C at all depths
# calculate fCO2 from pH and salinity-derived AT
  dplyr::select(datetime, depth, pHint_tot_sf, sal_insitu_ctd, temp_insitu_ctd) %>% 
  drop_na() %>% 
  dplyr::mutate(at_0_4m = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
                pco2_0_4m = seacarb::carb(flag=8, var1=pHint_tot_sf, var2=tmp$at_0_4m)$pCO2)
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
  tidyr::drop_na() %>% 
  dplyr::filter(depth_group != "NA") %>% 
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pHint_tot_sf at 4°C vs depth", x = "Depth (m)", y= "pH at 4°C (units)") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group * tmp$montht))

pH_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
  scale_x_discrete("Month", expand = c(0, 0)) +
  scale_y_continuous(substitute("pH"["T"] ~ "at 4°C"), limits = c(-0.2, 0.2), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.8, parse = TRUE, label = "pH['surface'] > pH['deep']") +
  annotate("text", x = 1.5, y = -0.15, parse = TRUE, label = "pH['surface'] < pH['deep']") +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
# all deltas
deltas_plt <- sal_delta_plt / temp_delta_plt / den_delta_plt / pH_delta_plt
deltas_plt <- deltas_plt + plot_annotation(tag_levels = 'a')
print(deltas_plt)
ggsave(filename = "figures/deltas.png", plot = deltas_plt, width = 15, height = 20, units = "cm")
```
